Public transport and school location impacts on educational inequalities: insights from São Paulo

### 2017-04-02 paper_v2.tex
Add why not using price

For this work we used the Google Matrix Distance API
(application programming interface), a multi-modal
real-time travel data provider (see \href{https://developers.google.com/maps/documentation/distance-matrix/}{developers.google.com/maps/}). 
The API was used in preference to other options,
such as Routino --- see Singleton (2014) for a used case involving large-scale accessibility analysis ---
and the OpenStreetMap Routing Machine (OSRM)
because its
ease of use (requiring no new software to be installed locally)
and performance: the Google Distance Matrix
API returns
route distance, price and times for journeys between origins and
destinations, provided either as Longitude/Latitude pairs or
as text strings to be 'geocoded' (converted to geographical location).

@@

The provision of a public transport subsidy for school commutes is
unlikely to compensate students at the bottom of the income and
accessibility ladder if the increase in commuting times has consequences in terms of motivation to stay in school and performance. In this sense, a ``trade-off'' logic where less schooling provision is compensated by public transport subsidies does not operate when existing inequalities in provision are large.

>>>>

For this work we used the Google Matrix Distance API
(application programming interface), a multi-modal
real-time travel data provider (see \href{https://developers.google.com/maps/documentation/distance-matrix/}{developers.google.com/maps/}). 
The API was used in preference to other options,
such as Routino --- see Singleton (2014) for a used case involving large-scale accessibility analysis ---
and the OpenStreetMap Routing Machine (OSRM)
because its
ease of use (requiring no new software to be installed locally)
and performance: the Google Distance Matrix
API returns
route distance, price (but not price for travel to school) and times for journeys between origins and
destinations, provided either as Longitude/Latitude pairs or
as text strings to be 'geocoded' (converted to geographical location).

@@

The provision of a public transport subsidy for school commutes is
unlikely to compensate students at the bottom of the income and
accessibility ladder if the increase in commuting times has consequences in terms of motivation to stay in school and performance. In this sense, a ``trade-off'' logic where less schooling provision is compensated by public transport subsidies does not operate when existing inequalities in provision are large.
The use of travel times rather than economic cost raises the question: is affordability or accessibility more important in affecting educational inequalities?
The focus on the time data from the Google Matrix API reflects the greater robustness of this measure (prices can fluctuate rapidly) and the fact that, thanks to the Free Pass Movement, there is a widespread perception that public transport to schools should be free. The analysis in this paper therefore assumes very low or zero financial cost for public transport to school.
